Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-05-19 experiments.tex
added dispersion pics

Set of Figures~\ref{fig:pareto_fronts_100}
and~\ref{fig:pareto_fronts} show the resultig pareto fronts for two
different scenarios of 100 and 500 simulations budget.

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{pictures/alloca_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/bmm_100.eps} & 
    \includegraphics[width=0.32\textwidth]{pictures/fir_int100.eps} \\
    \includegraphics[width=0.32\textwidth]{pictures/mm_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/sha_100.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/wave_100.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
  \label{fig:pareto_fronts_100}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{pictures/alloca_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/bmm_500.eps} & 
    \includegraphics[width=0.32\textwidth]{pictures/fir_int500.eps} \\
    \includegraphics[width=0.32\textwidth]{pictures/mm_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/sha_500.eps} &
    \includegraphics[width=0.32\textwidth]{pictures/wave_500.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
  \label{fig:pareto_fronts_100}
\end{table*}
Figures~\ref{fig:pareto_fronts_100} and~\ref{fig:pareto_fronts}
respectively show the visited configurations and the
Pareto fronts found for both FCP and VCP scenarios for different
application benchmarks. How it can be observed, VCP solutions
are on average  more widely and evenly distributed over the objective
space as compared to those found for the FCP case.

In order to evaluate the Paretos from a quantitative point-of-view we
will consider two metrics, namely, the \emph{variation range} and the
\emph{average normalised absolute dispersion error}. For a given
objective, the variation range represents the ratio between the
maximum and the minimum value observed for that objective. A
comparison between the variation range for different benchmarks
between a FCP and a VCP exploration for both power dissipation and
execution time is shown in Fig.~\ref{fig:variation_range}. As it can
be observed, the VCP exploration provides solutions which fall on a
range that is, on average, 23\% and 40\% wider than that provided by a
FCP exploration for power dissipation and execution time,
respectively.
\begin{figure}
  \centering
  \begin{tabular}{c}
    \includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} \\
    \includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps}
  \end{tabular}
  \caption{Variation range for different benchmarks between PS and GA
  exploration for power dissipation and execution time.}
  \label{fig:variation_range}
\end{figure}

@@

Fig.~\ref{fig:dispersion} shows the average normalised absolute
dispersion errors for different benchmarks for FCP and VCP
exploration. As it can be observed, VCP exploration reduces the
dispersion error on average by 20\% as compared to a FCP exporation.
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} \\
  \caption{Average normalised absolute dispersion errors for different
    benchmarks for FCP and VCP exploration.}
  \label{fig:dispersion}
\end{figure}

>>>>

Set of Figures~\ref{fig:pareto_fronts_100}
and~\ref{fig:pareto_fronts_500} show the resultig pareto fronts for two
different scenarios of 100 and 500 simulations budget.

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.30\textwidth]{pictures/alloca_100.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/bmm_100.eps} & 
    \includegraphics[width=0.30\textwidth]{pictures/fir_int100.eps} \\
    \includegraphics[width=0.30\textwidth]{pictures/mm_100.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/sha_100.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/wave_100.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 100 configurations.}
  \label{fig:pareto_fronts_100}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \includegraphics[width=0.30\textwidth]{pictures/alloca_500.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/bmm_500.eps} & 
    \includegraphics[width=0.30\textwidth]{pictures/fir_int500.eps} \\
    \includegraphics[width=0.30\textwidth]{pictures/mm_500.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/sha_500.eps} &
    \includegraphics[width=0.30\textwidth]{pictures/wave_500.eps} 
  \end{tabular}
  \caption{Pareto fronts found by PS and GA for a fixed budget of 500 configurations.}
  \label{fig:pareto_fronts_500}
\end{table*}

As can be seen TODO...

In order to evaluate the Paretos from a quantitative point-of-view we
will consider two metrics, namely, the \emph{variation range} and the
\emph{average normalised absolute dispersion error}. For a given
objective, the variation range represents the ratio between the
maximum and the minimum value observed for that objective. A
comparison between the variation range for different benchmarks
between a FCP and a VCP exploration for both power dissipation and
execution time is shown in Fig.~\ref{fig:variation_range}. As it can
be observed, the VCP exploration provides solutions which fall on a
range that is, on average, 23\% and 40\% wider than that provided by a
FCP exploration for power dissipation and execution time,
respectively.
\begin{table}
  \centering
  \begin{tabular}{c}
    \includegraphics[width=0.4\textwidth]{pictures/variation_power.eps} \\
    (a) \\
    \includegraphics[width=0.4\textwidth]{pictures/variation_etime.eps}
    (b) \\
    \includegraphics[width=0.4\textwidth]{pictures/dispersion.eps} \\
    (c) 
  \end{tabular}
  \caption{(a)(b) Variation range for different benchmarks between PS and GA
  and average dispersion absolute dispersion (c)}
  \label{fig:dispersion}
\end{table}

@@

Fig.~\ref{fig:dispersion}(c) shows the average normalised absolute
dispersion errors for different benchmarks for FCP and VCP
exploration. As it can be observed, VCP exploration reduces the
dispersion error on average by 20\% as compared to a FCP exporation.
